Global case

### 2025-05-07 lipschitz/Lipitschz.tex
update

@@

	We can modify the MILP model for local robustness to compute the question of global robustness \ref{global_robustness}.

	\subsection{Cloned model}

	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra variables and constraints:

>>>>

	The global structure is as follows, using Gurobi as an example:
	\begin{enumerate}
		\item For each input node, each output node, and each pre-activation and post-activation node in the hidden layers,  set one variable. 
		\item Set constraints for input nodes.
		\item For each pre-activation node in a hidden layer (and each output node), set linear constraints relating them to the post-activation or input nodes in the previous layer they connect to.
		\item Between pre- and post- activation nodes, set the MILP constraint described above.
	\end{enumerate} We use $\mathcal{M}$ to denote the whole MILP model. In practice, we may only consider the network up to a certain hidden layer. In that case, the pre-activation nodes of that layer serve as the output nodes of the model $\mathcal{M}$.

@@

	\subsection{Cloned model}
		We can modify the MILP model for local robustness to compute the question of global robustness \ref{global_robustness}.

	The most straight way is to build a model $\mathcal{M}^{large}$ based on two identical MILP models $\mathcal{M},\mathcal{M}'$ with completely disjoint variables (including inputs and outputs) with some extra constraints:

	\begin{enumerate}
		\item Add constraints for input nodes between $\mathcal{M},\mathcal{M}'$ for the requirement $|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon$.

		\item Set optimization target to be the difference of two variables of the same output node in two models $\mathcal{M},\mathcal{M}'$ (since we want to compute $\max|f(\boldsymbol{x}) -f(\boldsymbol{y}) |$).
	\end{enumerate}

	This model
